decompr: GVC decomposition in R

### 2015-02-02 draft.Rnw
Update draft.Rnw

>>>>

% Baast, enter part on how the package is flexible and can be adapted

Since GVCs constitute a fairly new field of research, there are many ways forward for its analysis. 
The next central step is to examine both in theory and empirically how GVC participation affects real economic activity. 
More specifically, it is very relevant to look at how, for instance, 
employment and economic growth react when countries join GVCs and what the factors are that determine a successful relationship. 
From the standpoint of developing and emerging countries a very interesting question is if GVCs simplify industrialization 
and the formation of comparative advantage 
while high-income countries might look for an additional push for their stagnating post-crisis economies. 
We hope that \textbf{decompr} can play a part in this field and promote it.
